%%-----------Acknowledgements---------------
\chapter*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgments} 

I would like to acknowledge and thank Dr. Sebastian Madgwick, his company xio-Technologies, and his staff for their efforts in developing small embedded data loggers.
The x-IMU3 became a major inspiration when it was announced earlier in 2023 and Seb was willing to chat with me about Thetis's design and its flaws.
He has also been open to me using the x-IMU3 API on my board and the x-IMU3 user manual as a basis for Thetis's manual.
His contributions and advice directly influenced version 2.0 of the firmware and the hardware revision F6.
I am grateful for his correspondence and look forward to continuing our discussions on a variety of ideas.

Secondly, I would like to thank the students of the classes I taught in Fall 2022 and Spring 2023.
They were instrumental in helping me formalize some of my notes for this thesis and helped test some early ideas.
I am especially grateful for the students who deployed Thetis in their Surf Engineering Analysis class and for their patience when Thetis did not work as intended.
I wish it worked better for them, but it gave invaluable insight into the potential application of Thetis.

Finally, I would like to thank my committee members, especially Drs. Wood and Weaver for keeping me on the path.
Their advice and support kept my on the path, even during its most twisting and trying times.
I also appreciate Dr. Gutierrez's consul in making sure Thetis was actually a usable product and motivating me to try and continually refine my design into the best it could be.